Inefficient Concessions and Mediation

### 2017-09-09 notes.tex
add revision notes to to-do and fix a typo in draft
update notes for progress on static version, other minor details

\vskip.3in
\un{June 6, 2017}\\
Want to develop result showing that mediator increases potential for peace
\begin{itemize}
	\item i.e. want to show mediator makes (Trust, Trust) and equilibrium over a larger parameter space than without mediator
\end{itemize}

@@

\vskip.5in
Will need to start by assuming that $\de_h <$ threshold where separating with no concessions works.

\vskip1in
Intermediate step for Theorem 4
\begin{itemize}
	\item Low type IC constraint to solve for equilibrium high type gift
	\item Already having shown $g_l = 0$, can set $g_h = g$ for simplicity of notation
	\item Also, since all the discount factors are for the low type, I'll let $\de_l = \de$
	\item For the case where $e=1$:

@@

\newpage
To-do list after Venice CesIfo 06/15/17:
\begin{itemize}
	\item Add discussion of intuitive criterion to text (if I end up needing it): out of eqm beliefs put zero weight on types that can never gain from deviating from a fixed eqm outcome
	\item Pin down whether it matters for mediator outcome if $c_h = c$ or $c_h = c(g)$
	\item Incorporate mediator result into text; re-organize text so it matches June presentation more closely
	\item Note for mediator result:
		\begin{itemize}
			\item For two high types to cooperate in the mechanism, need large enough gift to screen out low types. They're still just reporting, so don't give a gift if not matched with another high type. PLUS when they're exchanging gifts, the gifts will actually be used for good:
				\[
				  T(1+g) \geq (1-\de)[T(1+g) + W] + \de (W-D)
				\]
				\[
				  \de \geq \frac{W}{T + Tg + D}
				\]
				Note that this threshold is smaller than $\frac{W}{T + D}$, the one we get without concessions having material benefit / harm
		\end{itemize}
	\item Jim Fearon: maybe get rid of repeated game and just parameterize a one-shot game; he has a paper about concessions being used against you; he also gave me the reference for another one but I've forgotten it
	\item Someone who \textit{can't} cooperate under either $e=0$ or $e=1$ CAN cooperate under mediator
		\begin{itemize}
			\item In the absence of mediation, being able to burn money can help, but you still lose something
			\item I still have a question about the overall game: if $e=0$ provides higher welfare if it were enforceable but it's not, do we just go with $e=1$? This question goes away if I get rid of the repeated game.
			\item Some parameters. For all of these, I take $W=8$, $D=5$, $T=10$
				\begin{itemize}
					\item $p=.4, \de_l = .45, \de_h = \de_{STC} = .53$. Choose $e=1$, but $\de_1 = .65$
					\item $p=.3, \de_l = .45, \de_h = \de_{STC}  = .53$. Choose $e=1$, but $\de_1 > 1$; even worse at $p=.2$
					\item $p=.4, \de_l = .5, \de_h = \de_{STC} = .53$. Choose $e=1$, $\de_1 \geq .4$ (works fine)
					\item $p=.1, \de_l = .1, \de_h = \de_{STC} = .53$. Choose $e=0$, but $\de_0 \geq 6.7$
					\item $p=.05, \de_l = .5, \de_h = .7$. Choose $e=0$, but $\de_0 = 7.6$
					\item $p=.1, \de_l = .5, \de_h = .75$. Choose $e=0$, but $\de_0 = 6.7$ and $\de_1 \geq 3$
				\end{itemize}
		\end{itemize}
\end{itemize}
\end{document}

>>>>

\vskip.3in
\un{June 6, 2017}\\
Want to develop result showing that mediator increases potential for peace
\begin{itemize}
	\item i.e. want to show mediator makes (Trust, Trust) an equilibrium over a larger parameter space than without mediator
\end{itemize}

@@

\vskip.4in
Need to start by assuming that $\de_h <$ threshold where separating with no concessions works.
\begin{itemize}
	\item \textbf{Check to see whether Theorem 4 proof has to change.}
\end{itemize}

\vskip.4in
Intermediate step for Theorem 4
\begin{itemize}
	\item Low type IC constraint to solve for equilibrium high type gift
	\item Already having shown $g_l = 0$, can set $g_h = g$ for simplicity of notation
	\item Also, since all the discount factors are for the low type, I'll let $\de_l = \de$
	\item For the case where $e=1$:

@@

\newpage
To-do list after Venice CesIfo 06/15/17:
\begin{itemize}
	\item Add discussion of intuitive criterion to text (if I end up needing it): out of eqm beliefs put zero weight on types that can never gain from deviating from a fixed eqm outcome
	\item Pin down whether it matters for mediator outcome if $c_h = c$ or $c_h = c(g)$
	\item Incorporate mediator result into text; re-organize text so it matches June presentation more closely
	\item Note for mediator result:
		\begin{itemize}
			\item For two high types to cooperate in the mechanism, need large enough gift to screen out low types. They're still just reporting, so don't give a gift if not matched with another high type. PLUS when they're exchanging gifts, the gifts will actually be used for good:
				\[
				  T(1+g) \geq (1-\de)[T(1+g) + W] + \de (W-D)
				\]
				\[
				  \de \geq \frac{W}{T + Tg + D}
				\]
				Note that this threshold is smaller than $\frac{W}{T + D}$, the one we get without concessions having material benefit / harm
		\end{itemize}
	\item Jim Fearon: maybe get rid of repeated game and just parameterize a one-shot game (doens't work because concessions required for separation are too large; require future to recoup cost
		\begin{itemize}
			\item he has a paper about concessions being used against you; he also gave me the reference for another one but I've forgotten it
		\end{itemize}
	\item Someone who \textit{can't} cooperate under either $e=0$ or $e=1$ CAN cooperate under mediator
		\begin{itemize}
			\item In the absence of mediation, being able to burn money can help, but you still lose something
			\item I still have a question about the overall game: if $e=0$ provides higher welfare if it were enforceable but it's not, do we just go with $e=1$?
			\item Some parameters. For all of these, I take $W=8$, $D=5$, $T=10$
				\begin{itemize}
					\item $p=.4, \de_l = .45, \de_h = \de_{STC} = .53$. Choose $e=1$, but $\de_1 = .65$
					\item $p=.3, \de_l = .45, \de_h = \de_{STC}  = .53$. Choose $e=1$, but $\de_1 > 1$; even worse at $p=.2$
					\item $p=.4, \de_l = .5, \de_h = \de_{STC} = .53$. Choose $e=1$, $\de_1 \geq .4$ (works fine)
					\item $p=.1, \de_l = .1, \de_h = \de_{STC} = .53$. Choose $e=0$, but $\de_0 \geq 6.7$
					\item $p=.05, \de_l = .5, \de_h = .7$. Choose $e=0$, but $\de_0 = 7.6$
					\item $p=.1, \de_l = .5, \de_h = .75$. Choose $e=0$, but $\de_0 = 6.7$ and $\de_1 \geq 3$
				\end{itemize}
		\end{itemize}
	\item From Eli four years ago: why can mediator do what the two sides cannot?
		\begin{itemize}
			\item How does this differ from binding arbitration?
		\end{itemize}
	\item Be clear about assumptions on cost of gifts; make statement in third paragraph of model section match
\end{itemize}
\end{document}
